\subsection{Attempt to properly modularize PersonForm}
\begin{frame}[c]{Motivation for PersonForm abstraction}
    \begin{multicols}{2}
    \tiny
        \phantom{M}
    \large
        \begin{itemize}[<+(1)->]
            \item Boilerplate: strong indicator for bad code quality!
            \item Redundant!
            \item Prone to Bugs!
            \item Distracts from meaning!
            \item Not Flexible!
            \item Hard to modify!
        \end{itemize}
    \tiny
    \phantom{M}
    \inputminted[linenos,xleftmargin=2em]{python}{code/personform.py}
    \end{multicols}
\end{frame}

%     \begin{frame}[c]{PersonForm and Views}
%     So I created a ModelForm for Person.
%     And a Personformset.
%     And startet to integrate it in the OrderSimpleForm
%     \end{frame}

\begin{frame}[c]{Intermediate Results}
    \begin{multicols}{2}
        \tiny
        \inputminted[linenos]{python}{code/personforms.py}
        \normalsize
        \begin{itemize}[<+(1)->]
            \item Abstraction to one dedicated PersonForm
            \item PersonFormSet can have arbitrarily many Persons (was only five)
            \item Simplifies implementation in View
            \item Difficult to propagate ValidationErrors properly
            \item Would have deleted about 300 lines of boilerplate
            % \item Problem: A view is supposed to show only a single Form
                % \item Problem: Took a long time to implement
        \end{itemize}
    \end{multicols}
\end{frame}

\begin{frame}[c]{Reasons for Failure}
    % Managed to get quite far, very good (deep) learning example, and absolutely
    % possible. just requires some more time than expected.
    % Nags me that it's not modular yet. Some day.
    \large
    \begin{itemize}[<+(1)->]
        \item Nesting of \mintinline{python}{Forms} is \textbf{not} supported (\mintinline{python}{owner} within \mintinline{python}{OrderSimpleForm})
        \item Particularly with the many assumptions and automated parts of \mintinline{python}{ModelForm}s
        % \item Need to manually call all steps from other \mintinline{python}{ModelForm}
        \item Manually register fields for \mintinline{python}{ValidationErrors}
        \item Manually put in values for Validation (from \mintinline{python}{PersonFormSet})
        \item Manually take values out to save new Models
    \end{itemize}
    \pause
    Nothing impossible, but requires a lot of intricate details to get right.
    \pause
    We decided to instead implement something else.
\end{frame}

