
\section{What is it?}

\begin{frame}[c]{What is Rationality? Wikipedia}
    \pause
    \begin{qblock}{Wikipedia}
    Rationality is the quality or state of being rational – that is, being
    based on or agreeable to reason. \\

    "Rationality" has different specialized meanings in philosophy,
    economics, sociology, psychology, evolutionary biology, game theory and
    political science.
    \end{qblock}
\end{frame}


\begin{frame}[c]{What is Rationality? My answer}
    \Large
    \begin{itemize}[<+(1)->]
        \item Everything that can help you
        \item Extreme take on effectiveness
        \item When in a competition with someone else, I want to be more effective
        \item Everything, to ultimately \newline \textbf{achieve your goals}
    \end{itemize}
    \pnote{yes, EVERYTHING, and if a deal with the devil would allow us to
    achieve them, then we'll take that shortcut, obviously. Even if you have
    constraints, say, you want to achieve your goal but without making a deal
    with the devil. Might be better, since it's really hard to meet with the
    devil nowadays. Any one of his subcontractors should do for most goals.}
\end{frame}


\begin{frame}[c]{Rationality has two sides that need each other}
    \pause
    \begin{qblock}{Epistemic Rationality}
        Finding out what is true
    \end{qblock}

    \pause
    \vspace{1cm}

    \begin{qblock}{Instrumental Rationality}
        Achieving your goals
    \end{qblock}
\end{frame}


\begin{frame}[c]{This talk will focus on Epistemic Rationality}
    \Large
    It is rarely talked about Epistemic Rationality - which is why it will be the focus of this talk.
\end{frame}




\section{\LaTeX \phantom{ } Examples}

\begin{frame}[c]
     Here a citation: \cite{benchcpp}
\end{frame}




\begin{frame}[c]{Example slide}
    \pnote{The items to discuss are:
    - First Element \n
    - Second Element
    Later on, also:
    - Third Element
    }
    \pnote{Note in next line}
    \Large
    \begin{itemize}[<+->]
        \item Shows immediately!
        \item Second Element
        \item Third Element
    \end{itemize}
\end{frame}


\begin{frame}[c]{Element visible in handout only}
    \Large
    \begin{itemize}[<+(1)->]
        \item Delay of one slide!
        \item Second Element
        \item<handout> Only visible in Handout!
    \end{itemize}
    \pnote{The notes are visible BEFORE the slide in pdfpc!}
\end{frame}


\begin{frame}<handout:0>[c]{Not Visible in Handout}
    \Large
    \begin{itemize}[<+(1)->]
        \item These slides do not show in Handout
        \item Second Element
        \item Third Element
    \end{itemize}
\end{frame}


\begin{frame}[c]{Prevent Wobbeling}

    Simply use an overlayarea!

    % \begin{verbatim}
    %     \begin{overlayarea}{\textwidth}{0.8\textheight}
    %     \end{overlayarea}
    % \end{verbatim}

\end{frame}



